Market Expectations and Mangerial Turnover

### 2024-02-23 paper.qmd
some adaptions

```{python}
import pandas as pd
from pandas_profiling import ProfileReport

spells_raw = pd.read_csv("raw_data/club_manager_histories_df.csv")

# Generating a report
profile = ProfileReport(spells_raw, title="Profile data", explorative=True)

# To display the report within a Jupyter Notebook
profile.to_notebook_iframe()
```

@@

>>>>

```{r}
library(readxl)
spells_raw = read_csv("raw_data/club_manager_histories_df.csv")
skimr::skim(spells_raw)

@@

```{r}
logit_baseline |>
  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
         "Cumulative Relative Strength"=b_Standardized_CumRS)

          |>
  pivot_longer(!.draw &!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
  ggplot(aes(y = fixed_effect,
             x=draws)) +
  stat_slab() +
  labs(x="",
       title="Baseline model for probability of poaching",
       subtitle="Posterior probability distribution",
       y="Fixed Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)
